---
title: "EDA"
author: "Alex Dombowsky"
date: "4/1/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(purrr)
library(dplyr)
```

# Cleaning data

```{r}
# loading and cleaning
temp = list.files(pattern="*.csv")
opiod = lapply(temp, read.csv)
names(opiod) = c("AD1", "ASD", "ASE", "ASF", "ASG", "ASI", "ASM", "ASP", "DEM", "DSM", "EOM", "FND", "INF", "LAB", "main", "MHX", "MOT", "NMS", 
                 "QLP", "QOL", "VIS")

# saving
save(opiod, file = "opiod.RData")
```

# Loading Data
```{r}
load("opiod.RData")
```

# Making into 1 data frame (might be useful)
```{r}
opiod_df <- opiod %>% reduce(full_join, by = "PATID")
```

# Notes on Design
## Initial Design
* CTN-0051 is an $N = 600$, multi-site, two arm, 6 month, parallel group, open label, randomized controlled trial to examine the comparitive effectiveness of XR-NTX vs. BUP-NX
* XR-NTX is administered by injection on an approximately every-four-week basis
* BUP-NX is provided for take-home daily sublingual dosing
* Recruitment completed in May, 2016, with N=772 participants consented, N=570 randomized (N=352 of them late randomizers). As of July 25, 2016, N=436 have completed the study

## Final Results
* Between Jan 30, 2014, and May 25, 2016, we randomly assigned 570 participants to receive XR-NTX (n=283) or BUP-NX (n=287).
* 204 participants inducted to XR-NTX treatment completed an average of 3·9 monthly injections (about 16 weeks treatment); 96 (47%) did not end medication early and completed the planned 24 week treatment phase
* 270 participants inducted to BUP-NX treatment completed a median of 14 weeks of treatment